More Tests

### 2022-11-23 Code/Block-Bootstrap.Rmd
Code

my_summary <- function(x)
{
  rm = rowMeans(x)
  c(rm, sd(x[1,]), rm[2] - sd(x[1,]), rm[6] - sd(x[1,]), (rm[2] - sd(x[1,])) / sd(x[1,]), (rm[6] - sd(x[1,])) / sd(x[1,]), rm[5] + qnorm(.975) * sqrt((rm[5] * (1 - rm[5])) / 1000), rm[5] - qnorm(.975) * sqrt((rm[5] * (1 - rm[5])) / 1000),  rm[9] + qnorm(.975) * sqrt((rm[9] * (1 - rm[9])) / 1000), rm[9] - qnorm(.975) * sqrt((rm[9] * (1 - rm[9])) / 1000))
}

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep2(400, 0, 0.1, 20, m1)))
root_norm_1 <- data.frame(c(400, 20, o))
for(l in 19:16)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(1000, do1rep2(n, 0, 0.1, l, m1)))
  root_norm_1 <- cbind(root_norm_1, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep2(225, 0, 0.1, 15, m1)))
root_norm_2 <- data.frame(c(225, 15, o))
for(l in 14:11)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(1000, do1rep2(n, 0, 0.1, l, m1)))
  root_norm_2 <- cbind(root_norm_2, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep2(100, 0, 0.1, 10, m1)))
root_norm_3 <- data.frame(c(100, 10, o))
for(l in 9:6)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(1000, do1rep2(n, 0, 0.1, l, m1)))
  root_norm_3 <- cbind(root_norm_3, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(400, 0, 0.1, 20, m1)))
root_0_1 <- data.frame(c(400, 20, o))
for(l in 19:16)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0, 0.1, l, m1)))
  root_0_1 <- cbind(root_0_1, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(225, 0, 0.1, 15, m1)))
root_0_2 <- data.frame(c(225, 15, o))
for(l in 14:11)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0, 0.1, l, m1)))
  root_0_2 <- cbind(root_0_2, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(100, 0, 0.1, 10, m1)))
root_0_3 <- data.frame(c(100, 10, o))
for(l in 9:6)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0, 0.1, l, m1)))
  root_0_3 <- cbind(root_0_3, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(400, 0.2, 0.1, 20, m1)))
root_0.2_1 <- data.frame(c(400, 20, o))
for(l in 19:16)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, l, m1)))
  root_0.2_1 <- cbind(root_0.2_1, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(225, 0.2, 0.1, 15, m1)))
root_0.2_2 <- data.frame(c(225, 15, o))
for(l in 14:11)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, l, m1)))
  root_0.2_2 <- cbind(root_0.2_2, c(n, l, t))
}

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(100, 0.2, 0.1, 10, m1)))
root_0.2_3 <- data.frame(c(100, 10, o))
for(l in 9:6)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, l, m1)))
  root_0.2_3 <- cbind(root_0.2_3, c(n, l, t))
}

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(625, 0.4, 0.1, 25, m1)))
root_0.4_1 <- data.frame(c(625, 25, o))
for(l in 24:21)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, l, m1)))
  root_0.4_1 <- cbind(root_0.4_1, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(400, 0.4, 0.1, 20, m1)))
root_0.4_2 <- data.frame(c(400, 20, o))
for(l in 19:16)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, l, m1)))
  root_0.4_2 <- cbind(root_0.4_2, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(225, 0.4, 0.1, 15, m1)))
root_0.4_3 <- data.frame(c(225, 15, o))
for(l in 14:11)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, l, m1)))
  root_0.4_3 <- cbind(root_0.4_3, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(100, 0.4, 0.1, 10, m1)))
root_0.4_4 <- data.frame(c(100, 10, o))
for(l in 9:6)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, l, m1)))
  root_0.4_4 <- cbind(root_0.4_4, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(900, 0.6, 0.1, 30, m1)))
root_0.6_1 <- data.frame(c(900, 30, o))
for(l in 29:26)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, l, m1)))
  root_0.6_1 <- cbind(root_0.6_1, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(625, 0.6, 0.1, 25, m1)))
root_0.6_2 <- data.frame(c(625, 25, o))
for(l in 24:21)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, l, m1)))
  root_0.6_2 <- cbind(root_0.6_2, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(400, 0.6, 0.1, 20, m1)))
root_0.6_3 <- data.frame(c(400, 20, o))
for(l in 19:16)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, l, m1)))
  root_0.6_3 <- cbind(root_0.6_3, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(225, 0.6, 0.1, 15, m1)))
root_0.6_4 <- data.frame(c(225, 15, o))
for(l in 14:11)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, l, m1)))
  root_0.6_4 <- cbind(root_0.6_4, c(n, l, t))

@@

print(root_0.6_4)
```
8 out of the 10 coverage rates are below .90.
```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep2(400, 0, 0.1, 10, m1)))
constant_norm_1 <- data.frame(c(400, 10, o))
for(m in 19:16)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(1000, do1rep2(n, 0, 0.1, 10, m1)))
  constant_norm_1 <- cbind(constant_norm_1, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep2(300, 0, 0.1, 10, m1)))
constant_norm_2 <- data.frame(c(300, 10, o))
for(m in 14:11)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(1000, do1rep2(n, 0, 0.1, 10, m1)))
  constant_norm_2 <- cbind(constant_norm_2, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep2(200, 0, 0.1, 10, m1)))
constant_norm_3 <- data.frame(c(200, 10, o))
for(m in 9:6)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(1000, do1rep2(n, 0, 0.1, 10, m1)))
  constant_norm_3 <- cbind(constant_norm_3, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep2(100, 0, 0.1, 10, m1)))
constant_norm_4 <- data.frame(c(100, 10, o))
for(m in 4:1)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(1000, do1rep2(n, 0, 0.1, 10, m1)))
  constant_norm_4 <- cbind(constant_norm_4, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(400, 0, 0.1, 10, m1)))
constant_0_1 <- data.frame(c(400, 10, o))
for(m in 19:16)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0, 0.1, 10, m1)))
  constant_0_1 <- cbind(constant_0_1, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(300, 0, 0.1, 10, m1)))
constant_0_2 <- data.frame(c(300, 10, o))
for(m in 14:11)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0, 0.1, 10, m1)))
  constant_0_2 <- cbind(constant_0_2, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(200, 0, 0.1, 10, m1)))
constant_0_3 <- data.frame(c(200, 10, o))
for(m in 9:6)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0, 0.1, 10, m1)))
  constant_0_3 <- cbind(constant_0_3, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(100, 0, 0.1, 10, m1)))
constant_0_4 <- data.frame(c(100, 10, o))
for(m in 4:1)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0, 0.1, 10, m1)))
  constant_0_4 <- cbind(constant_0_4, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(400, 0.2, 0.1, 10, m1)))
constant_0.2_1 <- data.frame(c(400, 10, o))
for(m in 19:16)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, 10, m1)))
  constant_0.2_1 <- cbind(constant_0.2_1, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(300, 0.2, 0.1, 10, m1)))
constant_0.2_2 <- data.frame(c(300, 10, o))
for(m in 14:11)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, 10, m1)))
  constant_0.2_2 <- cbind(constant_0.2_2, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(200, 0.2, 0.1, 10, m1)))
constant_0.2_3 <- data.frame(c(200, 10, o))
for(m in 9:6)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, 10, m1)))
  constant_0.2_3 <- cbind(constant_0.2_3, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(100, 0.2, 0.1, 10, m1)))
constant_0.2_4 <- data.frame(c(100, 10, o))
for(m in 4:1)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.2, 0.1, 10, m1)))
  constant_0.2_4 <- cbind(constant_0.2_4, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(600, 0.4, 0.1, 10, m1)))
constant_0.4_1 <- data.frame(c(600, 10, o))
for(m in 29:26)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
  constant_0.4_1 <- cbind(constant_0.4_1, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(500, 0.4, 0.1, 10, m1)))
constant_0.4_2 <- data.frame(c(500, 10, o))
for(m in 24:21)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
  constant_0.4_2 <- cbind(constant_0.4_2, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(400, 0.4, 0.1, 10, m1)))
constant_0.4_3 <- data.frame(c(400, 10, o))
for(m in 19:16)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
  constant_0.4_3 <- cbind(constant_0.4_3, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(300, 0.4, 0.1, 10, m1)))
constant_0.4_4 <- data.frame(c(300, 10, o))
for(m in 14:11)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
  constant_0.4_4 <- cbind(constant_0.4_4, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(200, 0.4, 0.1, 10, m1)))
constant_0.4_5 <- data.frame(c(200, 10, o))
for(m in 9:6)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
  constant_0.4_5 <- cbind(constant_0.4_5, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(100, 0.4, 0.1, 10, m1)))
constant_0.4_6 <- data.frame(c(100, 10, o))
for(m in 4:1)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.4, 0.1, 10, m1)))
  constant_0.4_6 <- cbind(constant_0.4_6, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(900, 0.6, 0.1, 10, m1)))
constant_0.6_1 <- data.frame(c(900, 10, o))
for(m in 44:41)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
  constant_0.6_1 <- cbind(constant_0.6_1, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(800, 0.6, 0.1, 10, m1)))
constant_0.6_2 <- data.frame(c(800, 10, o))
for(m in 39:36)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
  constant_0.6_2 <- cbind(constant_0.6_2, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(1000, do1rep(700, 0.6, 0.1, 10, m1)))
constant_0.6_3 <- data.frame(c(700, 10, o))
for(m in 34:31)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(1000, do1rep(n, 0.6, 0.1, 10, m1)))
  constant_0.6_3 <- cbind(constant_0.6_3, c(n, 10, t))

>>>>

my_summary <- function(x)
{
  rm = rowMeans(x)
  c(rm, sd(x[1,]), rm[2] - sd(x[1,]), rm[6] - sd(x[1,]), (rm[2] - sd(x[1,])) / sd(x[1,]), (rm[6] - sd(x[1,])) / sd(x[1,]), rm[5] + qnorm(.975) * sqrt((rm[5] * (1 - rm[5])) / 4000), rm[5] - qnorm(.975) * sqrt((rm[5] * (1 - rm[5])) / 4000),  rm[9] + qnorm(.975) * sqrt((rm[9] * (1 - rm[9])) / 4000), rm[9] - qnorm(.975) * sqrt((rm[9] * (1 - rm[9])) / 4000))
}

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep2(400, 0, 0.1, 20, m1)))
root_norm_1 <- data.frame(c(400, 20, o))
for(l in 19:16)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(4000, do1rep2(n, 0, 0.1, l, m1)))
  root_norm_1 <- cbind(root_norm_1, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep2(225, 0, 0.1, 15, m1)))
root_norm_2 <- data.frame(c(225, 15, o))
for(l in 14:11)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(4000, do1rep2(n, 0, 0.1, l, m1)))
  root_norm_2 <- cbind(root_norm_2, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep2(100, 0, 0.1, 10, m1)))
root_norm_3 <- data.frame(c(100, 10, o))
for(l in 9:6)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(4000, do1rep2(n, 0, 0.1, l, m1)))
  root_norm_3 <- cbind(root_norm_3, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(400, 0, 0.1, 20, m1)))
root_0_1 <- data.frame(c(400, 20, o))
for(l in 19:16)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(4000, do1rep(n, 0, 0.1, l, m1)))
  root_0_1 <- cbind(root_0_1, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(225, 0, 0.1, 15, m1)))
root_0_2 <- data.frame(c(225, 15, o))
for(l in 14:11)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(4000, do1rep(n, 0, 0.1, l, m1)))
  root_0_2 <- cbind(root_0_2, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(100, 0, 0.1, 10, m1)))
root_0_3 <- data.frame(c(100, 10, o))
for(l in 9:6)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(4000, do1rep(n, 0, 0.1, l, m1)))
  root_0_3 <- cbind(root_0_3, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(400, 0.2, 0.1, 20, m1)))
root_0.2_1 <- data.frame(c(400, 20, o))
for(l in 19:16)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(4000, do1rep(n, 0.2, 0.1, l, m1)))
  root_0.2_1 <- cbind(root_0.2_1, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(225, 0.2, 0.1, 15, m1)))
root_0.2_2 <- data.frame(c(225, 15, o))
for(l in 14:11)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(4000, do1rep(n, 0.2, 0.1, l, m1)))
  root_0.2_2 <- cbind(root_0.2_2, c(n, l, t))
}

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(100, 0.2, 0.1, 10, m1)))
root_0.2_3 <- data.frame(c(100, 10, o))
for(l in 9:6)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(4000, do1rep(n, 0.2, 0.1, l, m1)))
  root_0.2_3 <- cbind(root_0.2_3, c(n, l, t))
}

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(625, 0.4, 0.1, 25, m1)))
root_0.4_1 <- data.frame(c(625, 25, o))
for(l in 24:21)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(4000, do1rep(n, 0.4, 0.1, l, m1)))
  root_0.4_1 <- cbind(root_0.4_1, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(400, 0.4, 0.1, 20, m1)))
root_0.4_2 <- data.frame(c(400, 20, o))
for(l in 19:16)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(4000, do1rep(n, 0.4, 0.1, l, m1)))
  root_0.4_2 <- cbind(root_0.4_2, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(225, 0.4, 0.1, 15, m1)))
root_0.4_3 <- data.frame(c(225, 15, o))
for(l in 14:11)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(4000, do1rep(n, 0.4, 0.1, l, m1)))
  root_0.4_3 <- cbind(root_0.4_3, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(100, 0.4, 0.1, 10, m1)))
root_0.4_4 <- data.frame(c(100, 10, o))
for(l in 9:6)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(4000, do1rep(n, 0.4, 0.1, l, m1)))
  root_0.4_4 <- cbind(root_0.4_4, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(900, 0.6, 0.1, 30, m1)))
root_0.6_1 <- data.frame(c(900, 30, o))
for(l in 29:26)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(4000, do1rep(n, 0.6, 0.1, l, m1)))
  root_0.6_1 <- cbind(root_0.6_1, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(625, 0.6, 0.1, 25, m1)))
root_0.6_2 <- data.frame(c(625, 25, o))
for(l in 24:21)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(4000, do1rep(n, 0.6, 0.1, l, m1)))
  root_0.6_2 <- cbind(root_0.6_2, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(400, 0.6, 0.1, 20, m1)))
root_0.6_3 <- data.frame(c(400, 20, o))
for(l in 19:16)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(4000, do1rep(n, 0.6, 0.1, l, m1)))
  root_0.6_3 <- cbind(root_0.6_3, c(n, l, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(225, 0.6, 0.1, 15, m1)))
root_0.6_4 <- data.frame(c(225, 15, o))
for(l in 14:11)
{
  set.seed(5)
  n = l^2
  t = my_summary(replicate(4000, do1rep(n, 0.6, 0.1, l, m1)))
  root_0.6_4 <- cbind(root_0.6_4, c(n, l, t))

@@

print(root_0.6_4)
```
8 out of the 10 coverage rates are below .90.
```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep2(400, 0, 0.1, 10, m1)))
constant_norm_1 <- data.frame(c(400, 10, o))
for(m in 19:16)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(4000, do1rep2(n, 0, 0.1, 10, m1)))
  constant_norm_1 <- cbind(constant_norm_1, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep2(300, 0, 0.1, 10, m1)))
constant_norm_2 <- data.frame(c(300, 10, o))
for(m in 14:11)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(4000, do1rep2(n, 0, 0.1, 10, m1)))
  constant_norm_2 <- cbind(constant_norm_2, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep2(200, 0, 0.1, 10, m1)))
constant_norm_3 <- data.frame(c(200, 10, o))
for(m in 9:6)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(4000, do1rep2(n, 0, 0.1, 10, m1)))
  constant_norm_3 <- cbind(constant_norm_3, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep2(100, 0, 0.1, 10, m1)))
constant_norm_4 <- data.frame(c(100, 10, o))
for(m in 4:1)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(4000, do1rep2(n, 0, 0.1, 10, m1)))
  constant_norm_4 <- cbind(constant_norm_4, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(400, 0, 0.1, 10, m1)))
constant_0_1 <- data.frame(c(400, 10, o))
for(m in 19:16)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(4000, do1rep(n, 0, 0.1, 10, m1)))
  constant_0_1 <- cbind(constant_0_1, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(300, 0, 0.1, 10, m1)))
constant_0_2 <- data.frame(c(300, 10, o))
for(m in 14:11)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(4000, do1rep(n, 0, 0.1, 10, m1)))
  constant_0_2 <- cbind(constant_0_2, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(200, 0, 0.1, 10, m1)))
constant_0_3 <- data.frame(c(200, 10, o))
for(m in 9:6)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(4000, do1rep(n, 0, 0.1, 10, m1)))
  constant_0_3 <- cbind(constant_0_3, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(100, 0, 0.1, 10, m1)))
constant_0_4 <- data.frame(c(100, 10, o))
for(m in 4:1)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(4000, do1rep(n, 0, 0.1, 10, m1)))
  constant_0_4 <- cbind(constant_0_4, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(400, 0.2, 0.1, 10, m1)))
constant_0.2_1 <- data.frame(c(400, 10, o))
for(m in 19:16)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(4000, do1rep(n, 0.2, 0.1, 10, m1)))
  constant_0.2_1 <- cbind(constant_0.2_1, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(300, 0.2, 0.1, 10, m1)))
constant_0.2_2 <- data.frame(c(300, 10, o))
for(m in 14:11)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(4000, do1rep(n, 0.2, 0.1, 10, m1)))
  constant_0.2_2 <- cbind(constant_0.2_2, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(200, 0.2, 0.1, 10, m1)))
constant_0.2_3 <- data.frame(c(200, 10, o))
for(m in 9:6)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(4000, do1rep(n, 0.2, 0.1, 10, m1)))
  constant_0.2_3 <- cbind(constant_0.2_3, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(100, 0.2, 0.1, 10, m1)))
constant_0.2_4 <- data.frame(c(100, 10, o))
for(m in 4:1)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(4000, do1rep(n, 0.2, 0.1, 10, m1)))
  constant_0.2_4 <- cbind(constant_0.2_4, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(600, 0.4, 0.1, 10, m1)))
constant_0.4_1 <- data.frame(c(600, 10, o))
for(m in 29:26)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(4000, do1rep(n, 0.4, 0.1, 10, m1)))
  constant_0.4_1 <- cbind(constant_0.4_1, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(500, 0.4, 0.1, 10, m1)))
constant_0.4_2 <- data.frame(c(500, 10, o))
for(m in 24:21)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(4000, do1rep(n, 0.4, 0.1, 10, m1)))
  constant_0.4_2 <- cbind(constant_0.4_2, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(400, 0.4, 0.1, 10, m1)))
constant_0.4_3 <- data.frame(c(400, 10, o))
for(m in 19:16)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(4000, do1rep(n, 0.4, 0.1, 10, m1)))
  constant_0.4_3 <- cbind(constant_0.4_3, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(300, 0.4, 0.1, 10, m1)))
constant_0.4_4 <- data.frame(c(300, 10, o))
for(m in 14:11)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(4000, do1rep(n, 0.4, 0.1, 10, m1)))
  constant_0.4_4 <- cbind(constant_0.4_4, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(200, 0.4, 0.1, 10, m1)))
constant_0.4_5 <- data.frame(c(200, 10, o))
for(m in 9:6)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(4000, do1rep(n, 0.4, 0.1, 10, m1)))
  constant_0.4_5 <- cbind(constant_0.4_5, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(100, 0.4, 0.1, 10, m1)))
constant_0.4_6 <- data.frame(c(100, 10, o))
for(m in 4:1)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(4000, do1rep(n, 0.4, 0.1, 10, m1)))
  constant_0.4_6 <- cbind(constant_0.4_6, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(900, 0.6, 0.1, 10, m1)))
constant_0.6_1 <- data.frame(c(900, 10, o))
for(m in 44:41)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(4000, do1rep(n, 0.6, 0.1, 10, m1)))
  constant_0.6_1 <- cbind(constant_0.6_1, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(800, 0.6, 0.1, 10, m1)))
constant_0.6_2 <- data.frame(c(800, 10, o))
for(m in 39:36)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(4000, do1rep(n, 0.6, 0.1, 10, m1)))
  constant_0.6_2 <- cbind(constant_0.6_2, c(n, 10, t))

@@

```{r functions, echo = False}
set.seed(5)
o = my_summary(replicate(4000, do1rep(700, 0.6, 0.1, 10, m1)))
constant_0.6_3 <- data.frame(c(700, 10, o))
for(m in 34:31)
{
  set.seed(5)
  n = 20 * m
  t = my_summary(replicate(4000, do1rep(n, 0.6, 0.1, 10, m1)))
  constant_0.6_3 <- cbind(constant_0.6_3, c(n, 10, t))
